Simultaneous segmentation and distortion correction on diffusion weighted MR using shape priors

### 2012-12-12 Publications/2013-IPMI/Latex/00-Main.tex
added acknowledgments
but masked in main.tex for review. Please complete your own grants, and
maybe add Meri if apropriate (i.e. if removed from author list).
Fixed affiliations. Close #37, Close #38

\title{Simultaneous segmentation and distortion correction on diffusion weighted MR using shape priors}
%%
\titlerunning{Segmentation & EPI correction on DWI}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Oscar Esteban\inst{1,2} \and Alessandro Daducci \inst{2} \and
		Meritxell Bach-Cuadra \inst{2} \and Virginia Estellers \inst{2}
		\and Mar\'ia-Jes\'us Ledesma-Carbayo \and Luminita Vese \inst{3} \and 
        Jean-Philippe Thiran \inst{2} \and Andr\'es Santos \inst{1} \and
        Dominique Zosso \inst{2,3}}
%
\authorrunning{Oscar Esteban et al.} % abbreviated author list (for running head)

\institute{Biomedical Image Technologies (BIT),
ETSI Telecomunicaci\'on - Universidad Polit\'ecnica de Madrid
and CIBER-BBN, \\
Av. Complutense 30, E-28040 Madrid, Spain\\
\email{oscar.esteban@upm.es},\\
% WWW home page:
%\texttt{http://users/\homedir iekeland/web/welcome.html}
\and
Signal Processing Laboratory 5 (LTS5),
\'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL)\\
EPFL-STI-IEL-LTS5, Station 11, CH-1015 Lausanne, Switzerland
\and
Department of Mathematics, ... 
University of California Los Angeles (UCLA),
Los Angeles,..
}

>>>>

\title{Simultaneous segmentation and distortion correction on diffusion weighted MR using shape priors}
%%
\titlerunning{Segmentation & EPI correction on DWI}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Oscar Esteban\inst{1,2} \and
        Alessandro Daducci \inst{2} \and
		Meritxell Bach-Cuadra \inst{2,4} \and
		Mar\'ia-Jes\'us Ledesma-Carbayo \inst{1} \and 
        Jean-Philippe Thiran \inst{2,4} \and
        Andr\'es Santos \inst{1} \and
        Dominique Zosso \inst{3,2}}
%
\authorrunning{Oscar Esteban et al.} % abbreviated author list (for running head)

\institute{Biomedical Image Technologies (BIT),
ETSI Telecomunicaci\'on - Universidad Polit\'ecnica de Madrid
and CIBER-BBN, \\
Av. Complutense 30, E-28040 Madrid, Spain\\
\email{phd@oscaresteban.es},\\
% WWW home page:
%\texttt{http://users/\homedir iekeland/web/welcome.html}
\and
Signal Processing Laboratory (LTS5),
\'Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL)\\
EPFL-STI-IEL-LTS5, Station 11, CH-1015 Lausanne, Switzerland
\and
Department of Mathematics, 
University of California, Los Angeles (UCLA) \\
520 Portola Plaza, Box 951555, Los Angeles, CA 90095-1555, USA
\and
Department of Radiology, University Hospital Center (CHUV) and University of Lausanne (UNIL) \\
Rue du Bugnon 46, CH-1011 Lausanne, Switzerland
}
